---
title: "DATA 227: Stats Review Part B"
author: "Alex Kale"
date: "2023-05-09"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(readr)
library(dplyr)
library(tidyr)
library(ggplot2)
library(brms)
library(tidybayes)
library(ggdist)
```

## Loading the prepping the data

Let's get back to where we left off in terms of preparing the dataset.

```{r cars}
df = read_csv("../data/Titanic.csv", col_select = c("Name", "PClass", "Age", "Sex", "Survived"))
head(df)
```

```{r}
df = df |> 
  mutate(
    sex = if_else(Sex == "female", 1, 0),
    class = case_when(
      PClass == "1st" ~ 0,
      PClass == "2nd" ~ 1,
      TRUE            ~ 2)
  ) |> 
  drop_na()
head(df)
```
## A model with survived and sex as predictors

The next step in our model expansion workflow.

```{r}
m2 = brm(
  bf("Age ~ Survived + sex"),
  family = "lognormal",
  data = df,
  iter = 2000, warmup = 1000, chains = 2)
```

```{r}
summary(m2)
```

```{r}
plot(m2)
```

```{r}
pairs(m2)
```

Inferential and predictive uncertainty

```{r}
m2est_df = df |> 
  add_epred_draws(m2, ndraws = 200)

head(m2est_df)
```

```{r}
df %>%
  ggplot(aes(x = Age, y = as.factor(sex))) +
  stat_halfeye(aes(x = .epred), scale = 0.6, position = position_nudge(y = 0.175), data = m2est_df) +
  geom_point(position = position_jitter(height = 0.1), alpha = 0.6, data = df) +
  scale_color_brewer() +
  facet_grid(. ~ Survived) +
  theme_bw()
```

```{r}
m2pred_df = df %>%
  add_predicted_draws(m2, ndraws = 200)

head(m2pred_df)
```

```{r}
df %>%
  ggplot(aes(x = Age, y = as.factor(sex))) +
  stat_interval(aes(x = .prediction), position = position_nudge(y = 0.175), data = m2pred_df) +
  geom_point(position = position_jitter(height = 0.1), alpha = 0.6, data = df) +
  scale_color_brewer() +
  facet_grid(. ~ Survived) +
  theme_bw()
```

Maybe we need to add class and interactions with it.

## A model with class and interactions

Skipping a step or two in our model expansion workflow. Need to backtrack if something goes wrong.

```{r}
m3 = brm(
  bf("Age ~ Survived * sex * class"),
  family = "lognormal",
  data = df,
  iter = 2000, warmup = 1000, chains = 2)
```

```{r}
summary(m3)
```

```{r}
plot(m3)
```

```{r}
pairs(m3)
```

Inferential and predictive uncertainty

```{r}
m3est_df = df |> 
  add_epred_draws(m3, ndraws = 200)

head(m3est_df)
```

```{r}
df %>%
  ggplot(aes(x = Age, y = as.factor(sex))) +
  stat_halfeye(aes(x = .epred), scale = 0.6, position = position_nudge(y = 0.175), data = m3est_df) +
  geom_point(position = position_jitter(height = 0.1), alpha = 0.6, data = df) +
  scale_color_brewer() +
  facet_grid(class ~ Survived) +
  theme_bw()
```

```{r}
m3pred_df = df %>%
  add_predicted_draws(m3, ndraws = 200)

head(m3pred_df)
```

```{r}
df %>%
  ggplot(aes(x = Age, y = as.factor(sex))) +
  stat_interval(aes(x = .prediction), position = position_nudge(y = 0.175), data = m3pred_df) +
  geom_point(position = position_jitter(height = 0.1), alpha = 0.6, data = df) +
  scale_color_brewer() +
  facet_grid(class ~ Survived) +
  theme_bw()
```

In R, a very wide range of uncertainty visualizations are expressible. This is especially helpful for handling model outputs.
See http://mjskay.github.io/tidybayes/articles/tidy-brms.html#posterior-means-and-predictions


